### 2016-11-29 Paper_v1.tex
flux KO

To investigate the differences in carbon yields, we compared the flux distributions predicted by ssFBA simulations for the different constraint cases  (Fig.~\ref{fig:Network}).
The constrained cases (ii \& iii) heavily utilized the first step in the pentose phosphate pathway to generate NADPH;
the carbon flux then continued through the Entner–Doudoroff pathway toward pyruvate.
For case ii, the majority of the flux proceeded toward acetate accumulation, whereas in case iii, the flux accumulated as pyruvate, lactate, and acetate with some flux through the TCA cycle.
In comparison, the unconstrained case (i) showed the majority of flux traveling through glycolysis towards pyruvate, leading to accumulation of lactate, acetate and malate.
In all cases, the energy source was primarily oxidative phosphorylation, and to a lesser extent the TCA cycle.
However, the accumulation of acetate and lactate signifies that the system is not operating at its highest efficiency.
The system produced NADH through lactate dehydrogenase as well as through pyridine nucleotide transhydrogenase (\textit{pntAB}) to power oxidative phosphorylation.
Oxidative phosphorylation lead to a high redox ratio contributing to the accumulation of acetate overflow and diverting flux away from the TCA cycle.
This suggested CAT production could be increased by reducing the accumulation of acetate and lactate.
To investigate this further, we simulated potential knockouts with constrained transcription/translation rates.
Knocking out the \textit{gnd} reaction decreased acetate flux by more than half.
In addition, less uptake of amino acids were required which increased the carbon yield of CAT by 2\% (up to approximately 8\%) compared to the control (no knockouts).
The simulation showed an increase in oxidative phosphorylation flux and the majority of flux traveling through the pentose phosphate pathway.
A second simulation with both \textit{gnd} and phosphate acetyltransferase knocked out,
showed less carbon was needed to meet the translation bound, which increased the carbon yield by 6\% compared to the control (up to approximately 14\%).
In the dual knockout, flux towards acetate was mostly coming from amino acid degradation.
Sixty percent of the carbon flux traveled through glycolysis, while the remaining traveled through the pentose phosphate pathway.
This was similar to the flux distribution of the unconstrained case (case i).
Taken together, the dual knockout decreased acetate production and required less amino acid consumption, thus it is a promising strategy to increase the CAT carbon yield.
\textcolor{red}{MIKE: CAN WE GET A FIGURE THAT SHOWS THE KO FLUXES -and- WHAT ARE THE ERRORS ON THE YIELDS?}

@@

Knockouts of \textit{gnd} and phosphate acetyltransferase show that carbon can be diverted away from acetate and potentially toward CAT or other proteins of interest expressed in CFPS.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{./Figures/CAT_flux_final.pdf}
\caption{Flux profile for glycolysis, pentose phosphate pathway, Entner-Doudoroff pathway, TCA cycle, NADPH/NADH transfer, and oxidative phosphorylation. Sequence-specific FBA flux value (mean ± standard deviation) across ensemble for 1 hr, normalized to glucose uptake flux. Flux distribution for three different cases: unconstrained except for glucose uptake (top row), constrained by transcription and translation rates (second row), and constrained by transcription, translation rates and experimental measurements where available (bottom row).}
\label{fig:Network}
\end{figure}

>>>>

To investigate the differences in carbon yields, we compared the flux distributions predicted by ssFBA simulations for the different constraint cases  (Fig.~\ref{fig:Network}).
The constrained cases (ii \& iii) heavily utilized the first step in the pentose phosphate pathway to generate NADPH;
the carbon flux then continued through the Entner–Doudoroff pathway toward pyruvate.
For case ii, the majority of the flux proceeded toward acetate accumulation, whereas in case iii, the flux accumulated as pyruvate, lactate, and acetate with some flux through the TCA cycle.
In comparison, the unconstrained case (i) showed the majority of flux traveling through glycolysis towards pyruvate, leading to accumulation of lactate, acetate and malate.
In all cases, the energy source was primarily oxidative phosphorylation, and to a lesser extent the TCA cycle.
However, the accumulation of acetate and lactate signifies that the system is not operating at its highest efficiency.
The system produced NADH through lactate dehydrogenase as well as through pyridine nucleotide transhydrogenase (\textit{pntAB}) to power oxidative phosphorylation.
Oxidative phosphorylation lead to a high redox ratio contributing to the accumulation of acetate overflow and diverting flux away from the TCA cycle.
This suggested CAT production could be increased by reducing the accumulation of acetate and lactate.
To investigate this further, we simulated potential knockouts with constrained transcription/translation rates  (Fig.~\ref{fig:flux_ko}).
Knocking out the \textit{gnd} reaction, the first step in Entner-Doudoroff pathway, decreased acetate flux by about half.
In addition, less uptake of amino acids were required which increased the carbon yield of CAT by 2.7\% (up to approximately 25.3\% $\pm$ 3.6\%) compared to the control (no knockouts).
The simulation showed an increase in oxidative phosphorylation flux and the flux splitting between glycolysis and pentose phosphate pathway.
A second simulation with both \textit{gnd} and phosphate acetyltransferase knocked out,
showed less carbon was needed to meet the translation bound, which increased the carbon yield by 4\% compared to the control (up to approximately 26.7\% $\pm$ 3.4\%).
In the dual knockout, flux towards acetate was almost negligible with some coming from amino acid degradation.
Sixty-one percent of the carbon flux traveled through glycolysis, while the remaining traveled through pentose phosphate pathway.
This was similar to the flux distribution of the unconstrained case (case i).
Taken together, the dual knockout decreased acetate production and required less amino acid consumption, thus it is a promising strategy to increase the CAT carbon yield.

@@

Knockouts of \textit{gnd} and phosphate acetyltransferase show that carbon can be diverted away from acetate and toward CAT or other proteins of interest expressed in CFPS.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/CAT_flux_final.pdf}
\caption{Flux profile for glycolysis, pentose phosphate pathway, Entner-Doudoroff pathway, TCA cycle, NADPH/NADH transfer, and oxidative phosphorylation. Sequence-specific FBA flux value (mean ± standard deviation) across ensemble for 1 hr, normalized to glucose uptake flux. Flux distribution for three different cases: unconstrained except for glucose uptake (top row), constrained by transcription and translation rates (second row), and constrained by transcription, translation rates and experimental measurements where available (bottom row).}
\label{fig:Network}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/CAT_flux_ko.pdf}
\caption{Flux profile with knockouts for glycolysis, pentose phosphate pathway, Entner-Doudoroff pathway, TCA cycle, NADPH/NADH transfer, and oxidative phosphorylation. Sequence-specific FBA flux value (mean ± standard deviation) across ensemble for 1 hr, normalized to glucose uptake flux. Flux distribution for three different cases: constrained by transcription and translation rates (top row), constrained by transcription and translation rates with \textit{gnd} knocked out (second row), and constrained by transcription and translation rates with \textit{gnd} and phosphate acetyltransferase knocked out.}
\label{fig:flux_ko}
\end{figure}
